\documentclass[10pt, twocolumn,letterpaper]{article}
%\usepackage[margin=1in]{geometry}
\usepackage{cvpr}
%\usepackage{graphicx}
\usepackage[font=small, labelfont=bf]{caption}
\usepackage{subcaption}
%\usepackage{hyperref}
%\usepackage{xcolor}
%\usepackage{nameref}
%\usepackage{multirow}
%\usepackage{amsmath}
%\usepackage{mathtools}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage[breaklinks=true,bookmarks=false]{hyperref}
\usepackage[sorting=none, maxcitenames=2]{biblatex}
\addbibresource{bibliography.bib}
\setlength{\parindent}{0pt}

\cvprfinalcopy

% Title Page
\title{Hand-Drawn Graph Recognition\\
	ECE-549 / CS-543\\
	Project Report}
\author{Debopam Sanyal (dsanyal2) \and Neeraj Gangwar (gangwar2) \and Bryan Huang (bryanh2)}
% \date{}


\begin{document}
	\maketitle
	
	\input{./introduction.tex}
	
	\input{./segmentation.tex}
	
	\input{./classification.tex}
	
	\input{./interpretation.tex}
	
	\section{Conclusion and Future Work}
	In this project, we worked on the online graph recognition problem. For offline recognition, we tried to use the same pipeline by converting an offline graph to a sequence of coordinates. But this approach was not successful as the current pipeline heavily relies on the ordering of the coordinates. The offline recognition problem can be modeled as a learning problem and deep learning approaches can be used to solve it.\\
	
	The segmentation algorithms discussed in this report heavily rely of hyperparameter tuning. The values of these parameters can vary from person-to-person. Rather than finding the parameter values that work for everyone, we can tune these parameter for an individual by taking feedback from the user. The speed-based segmentation can be explored further. To reduce the false-positives, an abnormality computation step similar to the curvature-based segmentation can be added to overcome the noise.\\
	
	For classification, we found that it was a task well-suited to multiple pipeline configurations, only needing to adjust the input format. The geometric feature approach described in the original paper was the most effective. The problem is simple enough that attempting convolutional methods introduces significant complexity for minimal increase in efficacy.\\
    
  Classification is simple enough not to need an approach more complex than the features discussed here, but it is closely related to segmentation. Future work could include an object detection method to perform both tasks simultaneously.\\

  Interpretation depends heavily on segmentation and classification for accuracy. The main portions of interpretation are establishing vertex-edge and arrow-edge connections, scoring candidate graphs, and calculating the cost of an interpreted graph. From our results, we can see that vertices and edges were easier to deal with than arrows and loops. Future work would involve improving on the isomorphism function that we have. Another potential area is to experimentally determine threshold values. Another obvious area of development is building the offline method. There are some fundamentally different aspects to the offline method like the recognizer will only act on the graph after completion of all strokes and intermediate subgraphs do not have to be maintained in a locked-in graph. We found out that the cost function is not the best metric to evaluate our methods. It assigns full cost even to a graph with just one incorrect component. Thus, developing another quantitative performance evaluation metric for hand-drawn graphs is something that we want to work on in the future.\\
    
  In the current pipeline, the output needs to be evaluated by inspecting probabilities and costs.  It can be replaced with a user interface to visualize the output. It is a required feature for the end-user and will significantly reduce the time to analyze the performance of this pipeline.
	
	\section{Member Roles}
	Neeraj: segmentation, Bryan: classification, Debopam: interpretation and training. All of us worked on integrating the subparts into a whole. We used Github to maintain and share data (\href{https://github.com/neerajgangwar/graph-recognition}{Github Repository}). We met once a week to discuss updates and issues.
	
	\printbibliography[title=References]
	
\end{document}
